Exploiting the Social Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-27 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Adds another utility package
And some corrections here and there.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

@@

The remainder of this paper is organized as follows.
Section \ref{sec:interactive} presents related work on the topic 
of Interactive Evolution.
Then, Section \ref{sec:evospace-i} presents the computational platform on which 
the main proposal of this work is developed. The proposed graph model is 
presented in Section \ref{sec:graph}.
The experimental work and results are presented in Section \ref{sec:experiments}.
Finally, a concluding remarks are provided in Section \ref{sec:conclusions}.

@@

% Add something at the end linking with the next paragraph
% Done - Mario
The interaction between these entities are represented by the following relationships 
between nodes:

>>>>

% *** CITATION PACKAGES ***
%
\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

@@

The remainder of this paper is organized as follows.
Section \ref{sec:interactive} presents related work on the topic 
of Interactive Evolution.
Then, Section \ref{sec:evospace-i} presents the computational platform on which 
the main proposal of this work is developed. The proposed graph model is 
presented in Section \ref{sec:HCF}.
The experimental work and results are presented in Section \ref{sec:experiments}.
Finally, a concluding remarks are provided in Section \ref{sec:conclusions}.

@@

% Add something at the end linking with the next paragraph
% Done - Mario
The interaction between these entities and how they are represented by relationships 
between nodes are presented in the next subsection.
